\thesistitle

### 2019-07-17 sections/clonerefactor.tex
Changed the equality array image and added a table
Explain example

>>>>

The equality array for each of the lines in this example is shown in table \ref{table:equalityarrays}.

\begin{table}[H]
\begin{center}
 \caption{The equality arrays in our example figure \ref{fig:equalityarrays}.} \label{table:equalityarrays}
 \medskip
\begin{tabular}{|l|l|l|}
\hline
Node (N) & Equality Array (E)     & Size (S) \\ \hline
1        & {[}1, -2, 3, -5, -6{]} & 5        \\ \hline
2        & {[}1, -2, 7, -5, -6{]} & 5        \\ \hline
3        & {[}1, -2, 3, -5, -6{]} & 5        \\ \hline
4        & {[}8, -2, 7, -5, -6{]} & 5        \\ \hline
\end{tabular}
\end{center}
\end{table}

In the example of figure \ref{fig:equalityarrays} the fragment on the left (consisting of N_1 and N_2) and the fragment on the right (consisting of N_3 and N_4) are two clone instances of a clone class. We calculate the variability between two nodes by the following formula:

\begin{equation}\label{eq:removeexisting}
\{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S = S \cup C_{new}
\end{equation}
%Two nodes are considered clones of each other if the size of their equality array is equal and all negative numbers in the equality array are equal.
